---
title: "R Notebook"
output: html_notebook
---

```{r}
library(ggplot2)
library(lattice)
library(grid)
library(gridExtra)
library(cowplot)
library(dplyr)
```

1. turn nums count to proportions
```{r}
nums = read.csv("./preg_nums.csv")
nums[-1] <- nums[-1] / rowSums(nums[-1]) # get proportions by the row
inputcols = length(colnames(nums))
```

2. grab metadata
```{r}
metadata = read.csv("./metadata/samples_3.csv")
props = merge(nums, metadata[c("orig.ident","donor", "timepoint")], by.x = "X", by.y = "orig.ident", all.X = TRUE, all.y = FALSE)
levels(props$timepoint) = c("NP", "Pre", "T1", "T2", "T3", "Post")
extraCols = length(colnames(props)) - inputcols
```

#single graph test work (IGNORE)
```{r}
colnames(props)
ggplot(props, aes(timepoint, CD8_T, color = NA)) +
  geom_line(aes(color = donor)) + 
  geom_smooth(aes(color = donor)) + 
    geom_jitter() +
    stat_boxplot(fill = NA) +
  labs(subtitle = "CD8_T proportions by group")

```


3. really cool function to loop through graphs!! YAY 
```{r}
cellTypes = colnames(props)
cellTypesinterested = cellTypes[2:(length(cellTypes) - extraCols)]
myplots <- vector('list', length(cellTypesinterested))
t = 1
for (i in cellTypesinterested) {
    myplots[[t]] <- local({
        i <- i
        p1 <- ggplot(props, aes(timepoint, get(i), color = factor(timepoint))) + stat_boxplot(fill = NA) + geom_jitter() + ylab(i) + labs(subtitle = bquote(.(i) ~ ' proportions by group'))

        print(p1)
        t = t + 1
    })
}
```


4 lines
really cool function to loop through graphs!! YAY 
```{r}
cellTypes = colnames(props)
cellTypesinterested = cellTypes[2:(length(cellTypes)-extraCols)]
myplots <- vector('list', length(cellTypesinterested))
t = 1
for (i in cellTypesinterested) {
    myplots[[t]] <- local({
        i <- i
        p1 <- ggplot(props, aes(timepoint, get(i), fill=timepoint)) + geom_point(aes(fill = timepoint))+ geom_line(aes(group=donor, color = donor)) + ylab(i) + labs(subtitle = bquote(.(i) ~ ' proportions by group'))
        print(p1)
        t = t + 1
    })
}

```

## WITH THE SEURAT NUMS

1. turn nums count to proportions
```{r}
nums = read.csv("./output/preg_seuratNums.csv")
View(nums)
nums[-1] <- nums[-1] / rowSums(nums[-1]) # get proportions by the row
inputcols = length(colnames(nums))
```

2. grab metadata
```{r}
metadata = read.csv("./metadata/samples_3.csv")
props = merge(nums, metadata[c("orig.ident","donor", "timepoint")], by.x = "X", by.y = "orig.ident", all.X = TRUE, all.y = FALSE)
levels(props$timepoint) = c("NP", "Pre", "T1", "T2", "T3", "Post")
extraCols = length(colnames(props)) - inputcols
```

#single graph test work (IGNORE)
```{r}
colnames(props)
 ggplot(props, aes(timepoint, X0, color = NA)) +
  geom_line(aes(color = donor)) + 
  geom_smooth(aes(color = donor)) + 
    geom_jitter() +
    stat_boxplot(fill = NA) +
  labs(subtitle = "CD8_T proportions by group")

```


3. really cool function to loop through graphs!! YAY 
```{r}
cellTypes = colnames(props)
cellTypesinterested = cellTypes[2:(length(cellTypes) - extraCols)]
myplots <- vector('list', length(cellTypesinterested))
t = 1
for (i in cellTypesinterested) {
    myplots[[t]] <- local({
        i <- i
        p1 <- ggplot(props, aes(timepoint, get(i), color = factor(timepoint))) + stat_boxplot(fill = NA) + geom_jitter() + ylab(i) + labs(subtitle = bquote(.(i) ~ ' proportions by group'))

        print(p1)
        t = t + 1
    })
}
```




4 lines
really cool function to loop through graphs!! YAY 
```{r}
cellTypes = colnames(props)
cellTypesinterested = cellTypes[2:(length(cellTypes)-extraCols)]
myplots <- vector('list', length(cellTypesinterested))
t = 1
for (i in cellTypesinterested) {
    myplots[[t]] <- local({
        i <- i
        p1 <- ggplot(props, aes(timepoint, get(i), fill=timepoint)) + geom_point(aes(fill = timepoint))+ geom_line(aes(group=donor, color = donor)) + ylab(i) + labs(subtitle = bquote(.(i) ~ ' proportions by group'))
        print(p1)
        t = t + 1
    })
}

```


5. put together in 1 pdf # doesn't work
```{r}
View(props)
View(mtcars)
ggplot(props, aes(timepoint,  fill=timepoint)) + geom_point(aes(fill = timepoint))+ geom_line(aes(group=donor, color = donor)) 
mt
mt + facet_grid(vars(timepoint))

mt <- ggplot(props, aes(timepoint, colour = factor(timepoint))) +
  geom_point()

mt + facet_grid(vars(timepoint), scales = "free")

```

